Multiple linear regression

### 2018-11-27 DATA606/Lab8/michael-multiple_regression.Rmd
Completed Lab 8

```{r scatter-score-bty_avg, eval = FALSE}
plot(evals$score ~ evals$bty_avg)
```

@@

    $\text{AvgProfScore} = 3.88034 + 0.06664 \times \text{AvgBeautyRating}$

@@

```{r bty-rel, eval = FALSE}
plot(evals$bty_avg ~ evals$bty_f1lower)
cor(evals$bty_avg, evals$bty_f1lower)
```

@@

```{r bty-rels, eval = FALSE}
plot(evals[,13:19])
```

@@

```{r twoLines, eval = FALSE}
multiLines(m_bty_gen)
```

@@

11. Which variable would you expect to have the highest p-value in this model? 
    Why? *Hint:* Think about which variable would you expect to not have any 
    association with the professor score.

@@

```{r m_full, eval = FALSE, tidy = FALSE}
m_full <- lm(score ~ rank + ethnicity + gender + language + age + cls_perc_eval 
             + cls_students + cls_level + cls_profs + cls_credits + bty_avg 
             + pic_outfit + pic_color, data = evals)
summary(m_full)
```

12. Check your suspicions from the previous exercise. Include the model output
    in your response.

13. Interpret the coefficient associated with the ethnicity variable.

14. Drop the variable with the highest p-value and re-fit the model. Did the
    coefficients and significance of the other explanatory variables change?
    (One of the things that makes multiple regression interesting is that
    coefficient estimates depend on the other variables that are included in
    the model.) If not, what does this say about whether or not the dropped
    variable was collinear with the other explanatory variables?

15. Using backward-selection and p-value as the selection criterion,
    determine the best model. You do not need to show all steps in your
    answer, just the output for the final model. Also, write out the linear
    model for predicting score based on the final model you settle on.

@@

@@

@@

@@

>>>>

```{r scatter-score-bty_avg}
plot(evals$score ~ evals$bty_avg)
```

@@

    $\widehat{score} = 3.88034 + 0.06664 \times \text{bty_avg}$

@@

```{r bty-rel}
plot(evals$bty_avg ~ evals$bty_f1lower)
cor(evals$bty_avg, evals$bty_f1lower)
```

@@

```{r bty-rels}
plot(evals[,13:19])
```

@@

```{r twoLines}
multiLines(m_bty_gen)
```

@@

11. Which variable would you expect to have the highest p-value in this model? 
    Why? *Hint:* Think about which variable would you expect to not have any 
    association with the professor score. **cls_profs.  The number of professors teaching a course should have little to no bearing on their score.**

@@

```{r m_full}
m_full <- lm(score ~ rank + ethnicity + gender + language + age + cls_perc_eval 
             + cls_students + cls_level + cls_profs + cls_credits + bty_avg 
             + pic_outfit + pic_color, data = evals)
summary(m_full)
```

12. Check your suspicions from the previous exercise. Include the model output
    in your response. 
    **cls_profs has the highest P value 0.77806 meaning this is not a statistically significant variable.**

13. Interpret the coefficient associated with the ethnicity variable. 
    **The students found professors that are not a minority get a higher score than those who are.  This finding is not statistically significant.**

14. Drop the variable with the highest p-value and re-fit the model. Did the
    coefficients and significance of the other explanatory variables change?
    (One of the things that makes multiple regression interesting is that
    coefficient estimates depend on the other variables that are included in
    the model.) If not, what does this say about whether or not the dropped
    variable was collinear with the other explanatory variables?
    **Yes the coefficients and significances changed slightly.  For example the ethnicity variable is now statistically significant.**
    ```{r}
    m_nearly_full <- lm(score ~ rank + ethnicity + gender + language + age + cls_perc_eval + cls_students + cls_level + cls_credits + bty_avg 
             + pic_outfit + pic_color, data = evals)
summary(m_nearly_full)
    ```

15. Using backward-selection and p-value as the selection criterion,
    determine the best model. You do not need to show all steps in your
    answer, just the output for the final model. Also, write out the linear
    model for predicting score based on the final model you settle on.
    **The formula is:**
    $\widehat{score} = 3.69 + 0.22 ethnicity + 0.20 gender - 0.01 age + 0.005 \text{cls_perc_eval} + \\0.53 \text{cls_credits} + 0.05 \text{bty_avg} - 0.17  \text{pic_color}$

    ```{r}
    m_best <- lm(score ~ ethnicity + gender + age + cls_perc_eval + cls_credits + bty_avg + pic_color, data=evals)
    summary(m_best)
    ```

@@

    ```{r}
    plot(m_best)
    ```

    **Linearity: Red line in Residuals vs Fitted somewhat flat so condition is met.**

    **Constant variation: Points in Residuals vs Fitted plot show no apparant pattern generally therefore the condition is met.***

    **Nearly normal residuals: Points on Q to Q plot fairly linear so this condition is met.  There is some issues at the tails though.**

@@

    **No because the responses are from the student's point-of-view so they are still  independent.**

@@

    **An attractive young white male who teaches a one credit class and gets most of the students to complete an evaluation featured on a black and white head shot.**

@@

    **No.  Only 6 people rated the beauty of the professors.  This is not a large enough sample size to generalize the model.**
